Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Section 5 header

\section{Issues in concrete restrictions from the literature}
\label{sec:issues-literature}
\info{The various papers and the tradeoffs they make}

In this section, we review some shortcomings of existing work on union and
intersection contracts. We start with the work of Keil and
Thiemann~\cite{KeilThiemannUnionIntersection} which is the first to propose a
lean\todo{Not the right word} semantics for union and intersection contracts. We
follow with the work Williams, Morris, and Wadler~\cite{RootCauseOfBlame} which
builds upon~\cite{KeilThiemannUnionIntersection} and introduces a simpler, more
uniform blame resolution.

% The existing work that previously researched and implemented
% union and intersection
% as dynamic checks have, in our eyes, different shortcomings
% that makes them suboptimal solutions.
% In this section, we informally present those issues,
% starting with the foundational paper by Keil and Thiemann
% \cite{KeilThiemannUnionIntersection}, then following to a recent
% work by Williams, Morris, and Wadler \cite{RootCauseOfBlame}, and
% finally going over some similar contracts available in the Racket
% programming language.

@@

In Section~\ref{sec:issues-sem}, we've seen that different calls to a function
with an union contract must share information: the behavior of one call is
influenced by the previous ones, as the function must pick one component of the
union to satisfy across all usages. Conversely, following the semantics of
overloading, each application of a function with an intersection contract can
select a different branch and is thus independent from the others. A general
contract composed of nested unions, intersections and higher-order contracts
appears to require complex book-keeping in order to correctly raise blame.

>>>>

\section{Pragmatic trade-offs}
\label{sec:issues-literature}

Despite the difficulties of Section~\ref{sec:issues-sem}, union and
intersection contracts are still sought after. In this section we turn
to existing systems with union and intersection contracts in the
literature and in implementations.

These systems all make trade-offs, sacrificing some features of union
and intersection contracts to preserve language features. We survey
and discuss those trade-offs and their implications.

@@

In Section~\ref{sec:issues-sem}, we've seen that different calls to a function
with a union contract must share information: the behavior of one call is
influenced by the previous ones, as the function must pick one component of the
union to satisfy across all usages. Conversely, following the semantics of
overloading, each application of a function with an intersection contract can
select a different branch and is thus independent from the others. A general
contract composed of nested unions, intersections and higher-order contracts
appears to require complex book-keeping in order to correctly raise blame.
